Development of a educational and sustainable robotic platform for children and adults

### 2013-10-23 doc/paper.tex
autocommited by makefile

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}

\usepackage{xcolor}
\usepackage{tabu}
\usepackage{colortbl}

\usepackage{pifont}
% Math

@@

@@

@@

\ding{72} \ding{73}
\subsection{Arduino Robot}
\begin{figure}[h!]
  \centering
  \includegraphics[width=0.5\textwidth]{images/arduinorobot.jpg}
  \caption{Picture of the Arduino Robot}
\end{figure}

>>>>

\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}

\usepackage{ifthen}
\usepackage{xcolor}
\usepackage{tabu}
\usepackage{colortbl}
\usepackage{calc}

\usepackage{pifont}
\usepackage{forloop}
\usepackage[nomessages]{fp}
% Math

@@

\newcounter{starnumber}
\newcommand{\stars}[1]{
  \forloop{starnumber}{1}{\value{starnumber} < 6}{
    \ifthenelse{#1 < \value{starnumber}}{\ding{73}}{\ding{72}}%
  }
}

@@

Assement criterias are evaluated using a rating system which allows values between zero and five where higher values are better. Each value is represented using stars for better overview. Detailed description of each rating is explained below.

\begin{description}
\item[\stars{5}] The evaluated aspect fully complies with the assessment critera and adds additional functionality which exceeds expectations. 
\item[\stars{4}] The evaluated aspect fully complies with the assessment critera. Mentioned properties may have minor restraints which do not affect the overall rating of the system.
\item[\stars{3}]foo
\item[\stars{2}]foo
\item[\stars{1}]foo
\item[\stars{0}] The evaluated aspect does not comply with 
\end{description}

@@

%\ding{72}\ding{73}

\subsection{Arduino Robot}
\begin{figure}[h!]
  \centering
  \includegraphics[width=0.5\textwidth]{images/arduinorobot.jpg}
  \caption{Picture of the Arduino Robot}
\end{figure}
